### 2022-07-25 src/text/2-package-subsections/makers.tex
Update makers sub-package description

\subsection{gammapy.makers}
\label{ssec:gammapy-makers}
\todo{Regis Terrier}

\begin{figure}
	\import{code-examples/generated/}{gp_makers}

	\caption{Using gammapy.makers to reduce DL3 level data into a
		\code{MapDataset}.}
	\label{ig*:minted:gp_makers}
\end{figure}

The data reduction contains all tasks required to process and prepare data at
the DL3 level for modeling and fitting. The \code{gammapy.makers} sub-package
contains the various classes and functions required to do so. First, events are
binned and IRFs are interpolated and projected onto the chosen analysis
geometry. This produces counts, exposure, background, psf and energy dispersion
maps. The \code{MapDatasetMaker} and \code{SpectrumDatasetMaker} are
responsible for this task, see Fig~\ref{ig*:minted:gp_makers}.

>>>>

\subsection{gammapy.makers}
\label{ssec:gammapy-makers}
%
\begin{figure}
	\import{code-examples/generated/}{gp_makers}

	\caption{
        Using \code{gammapy.makers} to reduce DL3 level data into a
		\code{MapDataset}. All \code{Maker} classes take
        the configuration on initialisation of the class.
    }
	\label{ig*:minted:gp_makers}
\end{figure}
%
The data reduction step includes all tasks required to process and prepare
\gammaray data from the DL3 level to modeling and fitting. The \code{gammapy.makers} sub-package
contains the various classes and functions required to do so. First, events are
binned and IRFs are interpolated and projected onto the chosen analysis
geometry. This produces counts, exposure, background, psf and energy dispersion
maps. The \code{MapDatasetMaker} and \code{SpectrumDatasetMaker} are
responsible for this task, see Fig~\ref{ig*:minted:gp_makers}.
